Reproducibility in plant pathology: where do we stand and a way forward

### 2022-05-01 analysis/paper/paper.Rmd
Use 'here' and reformat code chunk

p <- p + plot_annotation(tag_levels = "A",
                         title = "Bayesian posterior distributions of evaluation score models"
                         )

ggsave(filename = "../figures/Sparks et al Figure 1.eps",
       plot = p,
       width = 6,
       height = 6,
       units = "in",
       device = cairo_ps)
extrafont::embed_fonts(
   file = ("../figures/Sparks et al Figure 1.eps"),
   outfile = ("../figures/Sparks et al Figure 1.eps"),
   options = "-dEPSCrop"
)
knitr::include_graphics(path = "../figures/Sparks et al Figure 1.eps")
```

@@

```{r reproScore, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Reproducibility scores of 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialised journals. Where 0 was not reproducible in any fashion and a perfect score would be 100% as evaluated for four areas software citations, software availability, computational methods availability and data availability on a 0 to 3 scale and converted to a "}
p <-
  ggplot(data = rrpp, aes(x = reproducibility_score)) +
  geom_histogram(binwidth = 10,
                 fill = "black") +
  ggtitle("Reproducibility index value")

ggsave(filename = "../figures/Sparks et al Figure 2.eps",
       plot = p,
       width = 6,
       height = 6,
       units = "in",
       device = cairo_ps)
extrafont::embed_fonts(
   file = ("../figures/Sparks et al Figure 2.eps"),
   outfile = ("../figures/Sparks et al Figure 2.eps"),
   options = "-dEPSCrop"
)
knitr::include_graphics(path = "../figures/Sparks et al Figure 2.eps")
```

@@

```{r articleScores, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Aggregated article scores for each of the four categories, (A) shows computational methods availability 0 - not available or not mentioned to 3 - freely available online to anonymous users. (B) presents 'Software availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Expensive proprietary software that only institutions would typically purchase'; '2' was 'Used proprietary software that most individuals can afford (e.g., Excel) or SAS that is now available free for use with a university login'; and '3' was 'Used entirely open source and free software (e.g., R, Julia, Python)'; 'NA' indicates that no specialised software was necessary or used. (C) displays 'Software citated', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Software mentioned by name only'; '2' was 'Software cited with version number'; and '3' was 'All software components (SAS PROCs, R, Julia or Python packages, etc.) cited'; 'NA' indicates that no specialised software was necessary or used. (D) shows 'Data availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g. a methods paper.", cache=FALSE, fig.env='figure', out.width=0, out.height=0}
theme_set(theme_classic())

@@

p <- ggplot(rrpp_long, aes(x = as.factor(value))) +
  geom_bar(fill = "black") +
  ylab("Count") +
  xlab("Article Score") +
  ggtitle("Aggregated article scores") +
  facet_wrap(name ~ .)
p <- tag_facet(p = p, tag_pool = LETTERS, x = 5, family = "Arial")

ggsave(filename = "../figures/Sparks et al Figure 3.eps",
       plot = p,
       width = 6,
       height = 6,
       units = "in",
       device = cairo_ps)
extrafont::embed_fonts(
   file = ("../figures/Sparks et al Figure 3.eps"),
   outfile = ("../figures/Sparks et al Figure 3.eps"),
   options = "-dEPSCrop"
)
knitr::include_graphics(path = "../figures/Sparks et al Figure 3.eps")
```

@@

    node [shape = oval, style = filled, fillcolor = grey99, width = 1.2, fontname = Helvetica]
    Question

    node [shape = box, style = filled, fillcolor = grey99, width = 1.2, fontname = Helvetica]
    Methodology; Data; Analysis; Manuscript;

    node [shape = box, style = filled, fillcolor = grey90, width = 1.2, fontname = Helvetica]
    Description; Availability; Citation

@@

    Question->Methodology->Data->Analysis
    Analysis->Manuscript
    Methodology->Description
    Methodology->Citation
    Methodology->Availability
    Manuscript->Supplement
    Data->'Data File'->'Public Repository'
    Data->Metadata->'Public Repository'
    Analysis->'Binary Code'->Supplement
    Analysis->'Source Code'->'Public Repository'
    Data->'Binary File'->Supplement
  }",
  width = 1000,
  height = 750
))

rsvg_ps(svg = charToRaw(p), file = "../figures/Sparks et al Figure 4.eps")
extrafont::embed_fonts(
   file = ("../figures/Sparks et al Figure 4.eps"),
   outfile = ("../figures/Sparks et al Figure 4.eps"),
   options = "-dEPSCrop"
)

knitr::include_graphics(path = "../figures/Sparks et al Figure 4.eps")
```

>>>>

p <- p + plot_annotation(tag_levels = "A",
                         title = "Bayesian posterior distributions of evaluation score models")

ggsave(
  filename = here("analysis/figures/Sparks et al Figure 1.eps"),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here("analysis/figures/Sparks et al Figure 1.eps"),
  outfile = here("analysis/figures/Sparks et al Figure 1.eps"),
  options = "-dEPSCrop"
)
include_graphics(path = here("analysis/figures/Sparks et al Figure 1.eps"))
```

@@

```{r reproScore, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Reproducibility scores of 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialised journals. Where 0 was not reproducible in any fashion and a perfect score would be 100% as evaluated for four areas software citations, software availability, computational methods availability and data availability on a 0 to 3 scale and converted to a "}
p <-
  ggplot(data = rrpp, aes(x = reproducibility_score)) +
  geom_histogram(binwidth = 10,
                 fill = "black",
                 colour = "black") +
  xlab("Reproducibility score (%)")

ggsave(
  filename = here("analysis/figures/Sparks et al Figure 2.eps"),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here("analysis/figures/Sparks et al Figure 2.eps"),
  outfile = here("analysis/figures/Sparks et al Figure 2.eps"),
  options = "-dEPSCrop"
)
include_graphics(path = here("analysis/figures/Sparks et al Figure 2.eps"))
```

@@

```{r articleScores, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Aggregated article scores for each of the four categories, (A) shows computational methods availability 0 - not available or not mentioned to 3 - freely available online to anonymous users. (B) presents 'Software availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Expensive proprietary software that only institutions would typically purchase'; '2' was 'Used proprietary software that most individuals can afford (e.g., Excel) or SAS that is now available free for use with a university login'; and '3' was 'Used entirely open source and free software (e.g., R, Julia, Python)'; 'NA' indicates that no specialised software was necessary or used. (C) displays 'Software citated', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Software mentioned by name only'; '2' was 'Software cited with version number'; and '3' was 'All software components (SAS PROCs, R, Julia or Python packages, etc.) cited'; 'NA' indicates that no specialised software was necessary or used. (D) shows 'Data availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g. a methods paper.", cache=FALSE, fig.env='figure', out.width=0, out.height=0}

@@

p <- ggplot(rrpp_long, aes(x = as.factor(value))) +
  geom_bar(fill = "black") +
  ylab("Count") +
  xlab("Article Score") +
  ggtitle("Reproducibility criteria ranks") +
  facet_wrap(name ~ .)
p <- tag_facet(
  p = p,
  tag_pool = LETTERS,
  x = 5,
  family = "Arial",
  open = "",
  close = ""
)

ggsave(
  filename = here("analysis/figures/Sparks et al Figure 3.eps"),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here("analysis/figures/Sparks et al Figure 3.eps"),
  outfile = here("analysis/figures/Sparks et al Figure 3.eps"),
  options = "-dEPSCrop"
)
include_graphics(path = here("analysis/figures/Sparks et al Figure 3.eps"))
```

@@

    node [shape = oval, style = filled, fillcolor = grey99, width = 1.2, fontname = Arial]
    Question

    node [shape = box, style = filled, fillcolor = grey99, width = 1.2, fontname = Arial]
    Methodology; Data; Analysis; Manuscript;

    node [shape = box, style = filled, fillcolor = grey90, width = 1.2, fontname = Arial]
    Description; Availability; Citation

@@

    Question->Methodology->Data->Analysis
    Analysis->Manuscript
    Methodology->Description
    Methodology->Citation
    Methodology->Availability
    Manuscript->Supplement
    Data->'Data File'->'Public Repository'
    Data->Metadata->'Public Repository'
    Analysis->'Binary Code'->Supplement
    Analysis->'Source Code'->'Public Repository'
    Data->'Binary File'->Supplement
  }",
  width = 1000,
  height = 750
  )
)

rsvg_ps(svg = charToRaw(p),
        file = here("analysis/figures/Sparks et al Figure 4.eps"))
embed_fonts(
  file = here("analysis/figures/Sparks et al Figure 4.eps"),
  outfile = here("analysis/figures/Sparks et al Figure 4.eps"),
  options = "-dEPSCrop"
)

include_graphics(path = here("analysis/figures/Sparks et al Figure 4.eps"))
```
